\section{Charging Islands}
% How will the vehicle be charged (conductive/inductive, DC/AC, other)?

%     What is the charging technology to be used and the expected power level? Why?

%     What are the power electronics converters necessary? What are their power ratings? Describe their topology.

%     What is the power and voltage range of the (fast) charger and expected charger time? Does the EV have fast charging?

%     How will you facilitate inter-operability?

%     Where and when would a user want to charge a vehicle of this type?

\subsection{Rationale for 25 kV AC Overhead Catenary Power Transfer}

For the dynamic charging islands, the system must reliably transfer between 10 MW and 20 MW of power to a moving locomotive in a 50$^\circ$C Sahara Desert environment. After evaluating both inductive charging and overhead catenary systems, the overhead catenary architecture was selected as the only physically and mathematically feasible option. The selection is driven by critical thermal, electromagnetic, and electrical current constraints.

\subsubsection*{Thermal Management and Heat Dissipation}
Assuming a highly optimistic 95\% efficiency for a 20 MW power transfer, the system must continuously dissipate approximately 1 MW of waste heat. 

\begin{itemize}
    \item \textbf{Track-Side Infrastructure:} Inductive transmitter coils must be buried in desert sand or concrete, which act as thermal insulators. This creates a ``thermal trap'' that would require unfeasible underground liquid cooling to prevent the coils from melting their own insulation. Conversely, an overhead catenary system distributes this heat across 5 km of bare copper wire suspended in the open air, resulting in a highly manageable thermal load of approximately 200 W/m that is safely dissipated via passive ambient air cooling.
    \item \textbf{Power Transfer Interface:} Inductive receiver pads possess a fixed, enclosed surface area that would act as a concentrated heat sink, requiring massive onboard liquid cooling. The overhead pantograph mitigates contact-point melting through \textit{kinetic cooling}; by manually constraining the train's charging speed to a minimum of 25 km/h, the pantograph continuously slides across ``fresh,'' unheated wire, spreading the friction and electrical arcing heat dynamically along the track length.
\end{itemize}

\subsubsection*{Electromagnetic Safety and Chassis Integrity}
Transferring up to 20 MW of power wirelessly via induction generates massive stray magnetic fields. At this power scale, the magnetic flux would induce significant eddy currents in the train's steel chassis, the iron wheels, and the rails, effectively heating the locomotive structure like an induction stove and creating severe electrocution hazards. The overhead catenary system isolates the electrical current within dedicated, shielded high-voltage cables leading directly to the onboard rectifiers, keeping the thermal load strictly contained within the train's dedicated active liquid-cooling loops.

\subsubsection*{Transmission Standard and Current Constraints}
While a native low-voltage DC microgrid is highly efficient, the physical limits of the pantograph-to-wire contact point prohibit a purely DC catenary at this power scale. 
\begin{itemize}
    \item \textbf{The Amperage Limit:} Standard DC railway voltages (e.g., 750 V DC to 3 kV DC) are practically limited to around 3 MW. Attempting to push 20 MW at 3 kV DC would result in over 6,000 Amps of current. This extreme amperage exceeds the physical limits of standard heavy-rail pantographs and would instantly melt the copper contact point.
    \item \textbf{25 kV AC Standard:} By specifying a 25 kV AC overhead line, the track can comfortably deliver 20 MW while keeping the current strictly under 800 Amps. This falls well within the safe operational limits of standard high-speed and heavy-freight rail pantographs.
\end{itemize}

The 25 kV AC overhead catenary is the selected architecture because it naturally manages the 1 MW thermal penalty through spatial distribution and passive cooling, avoids electromagnetic interference with the train chassis, and maintains a safe contact current. Furthermore, adopting 25 kV AC aligns the microgrid with proven global industry standards for heavy freight and high-speed rail, ensuring commercial component availability, interoperability, and long-term mechanical reliability in the harsh Sahara environment.


\subsection{Solar PV Generation and Environmental Adaptation}

The energy generation subsystem is the primary power source for the off-grid charging islands. Due to the extreme environmental conditions of the Sahara Desert and the mechanical stresses of heavy-haul rail operations, a highly specialized PV architecture is required to ensure long-term system reliability.

\subsubsection*{1. Mechanical and Environmental Placement Strategy}
The PV arrays are intentionally set back 20--30 meters from the track-side rather than being placed between or directly adjacent to the rails. This design choice is necessitated by two primary factors:
\begin{itemize}
    \item \textbf{Vibration Mitigation:} The 22,000-tonne iron-ore trains generate significant ground-borne vibrations. Direct rail-side placement would lead to accelerated cell micro-cracking and solder-joint failure. A 20m setback provides sufficient soil-damping to protect the module's crystalline structure.
    \item \textbf{Dust and Occlusion Management:} Moving trains continuously shed iron-ore dust and lubricant aerosols. These particles are highly opaque and electrically conductive; buildup on modules would lead to severe shading losses and potential fire hazards. The setback minimizes the volume of train-generated particulates reaching the array surface.
\end{itemize}

\subsubsection*{2. Module Technology: Heterojunction (HJT) and Bifaciality}
Standard PERC (Passivated Emitter and Rear Cell) modules are rejected for this project due to their high temperature coefficients. Instead, the design specifies \textbf{Bifacial HJT Modules}.
\begin{itemize}
    \item \textbf{Thermal Resilience:} HJT cells possess a superior temperature coefficient of approximately -0.25\%/$^\circ$C. In desert conditions where module temperatures frequently exceed 70$^\circ$C, HJT panels maintain significantly higher conversion efficiency compared to standard technologies that lose $\sim$15\% of their rated power in similar heat.
    \item \textbf{Albedo Utilization:} The Sahara sand provides a high albedo (reflectivity) of 30--45\%. Bifacial modules capture reflected irradiance on their rear surface, providing a ``free'' power boost of 15--20\% without increasing the physical footprint of the array.
\end{itemize}

\subsubsection*{3. Maintenance and Autonomous O\&M}
In the desert, sand accumulation (soiling) is the single largest cause of yield degradation, potentially reducing output by up to 30\% if left uncleaned. To ensure consistent 10~MW delivery:
\begin{itemize}
    \item \textbf{Robotic Cleaning:} The arrays are equipped with autonomous, waterless robotic cleaners. These robots perform nightly dry-sweeping cycles to remove sand and dust without consuming local water resources or causing abrasive damage to the anti-reflective coatings.
\end{itemize}

\subsubsection*{4. Sizing and Auxiliary Load Management}
To ensure the system is self-sustaining, the total peak capacity ($kW_p$) of the array is oversized by 10--15\% beyond the charging requirements of the train. This overhead is dedicated to powering the \textbf{Auxiliary Power Supply (APS)}, which drives the active liquid-cooling pumps and energy management systems required to keep the stationary LTO battery banks within their safe operational temperature window during daylight hours.

\begin{table}[h!]
\centering
\caption{Solar PV Engineering Design Summary}
\label{table:pv_design}
\begin{tabular}{|l|l|l|}
\hline
\textbf{Design Element} & \textbf{Selection} & \textbf{Engineering Rationale} \\ \hline
Placement & 20--30m Setback & Vibration damping and iron-ore dust mitigation. \\ \hline
Cell Type & Heterojunction (HJT) & Low temp. coefficient (-0.25\%/$^\circ$C) for 50$^\circ$C ambient. \\ \hline
Module Style & Bifacial & Utilizes 30--45\% sand albedo for 15--20\% yield boost. \\ \hline
Cleaning & Waterless Robotics & Prevents up to 30\% yield loss from desert soiling. \\ \hline
Sizing & 10--15\% Oversize & Dedicated capacity for battery liquid-cooling loads. \\ \hline
\end{tabular}
\end{table}