\section{Future Developments}\label{sec:future_dev}

The project can be divided into two primary areas where future developments will have a significant impact: the charging islands and the train itself.

\subsection{Impact on the Charging Islands}
Currently, the charging islands are designed to produce solar energy exclusively for the train. However, as these islands are situated at stations within villages, the project could be expanded to provide energy to the entire community. This expansion could be transformative, as many rural areas still rely on fossil fuels for generators and heating or dont have access to energy at all \cite{DOMEGNI2022112298}. Such a development aligns with the increasing global deployment of home energy storage systems \cite{ElectrekArticle2024}, which would allow villagers to store excess energy and use it as needed.

A major advancement that would significantly increase storage efficiency is the development of batteries better suited for the extreme temperature ranges of the desert. This would reduce the auxiliary energy required for thermal management (cooling and heating), thereby increasing the overall efficiency of the system.

\subsection{Impact on the Train}
The same advancements in battery technology apply to the train. High-temperature-resilient batteries would allow the vehicle to operate more efficiently with a reduced energy load on its thermal management systems.

Additionally, the anticipated increase in power converter efficiency \cite{ChargedEVsArticle} represents a key development. Given that the train relies heavily on power electronics for its traction system, more efficient converters would have a substantial positive impact on the vehicle's total energy consumption.

Another potential advancement is the optimization of the DC bus voltage. Although the current 800~V architecture aligns with established electric vehicle standards, this specific application differs significantly from typical automotive use cases. Increasing the DC bus voltage to a higher level could improve overall efficiency by enabling more optimal motor operating points.